% !TeX root = ../main.tex

\chapter{Methodology}\label{chapter:methodology}

\textbf{Literature Review:} Comprehensive review covering multi-agent orchestration frameworks, AI applications in legal technology and contract management, and compliance-aware explainable AI frameworks.

\textbf{Prototype Development:} Functional MAS-based CLM prototype implementing specialized agents for different CLM tasks (drafting, analysis, compliance), centralized orchestration mechanisms, communication protocols, and enterprise integration interfaces. Core functionality includes drafting assistance, clause classification, compliance checks, and explainability features.

\textbf{Evaluation Framework:} Multi-dimensional assessment including quantitative metrics (task completion time, accuracy metrics, compliance adherence, system performance) and qualitative metrics (explainability evaluation, usability studies, trust assessment, acceptance measurement).

\textbf{Comparative Analysis:} Systematic comparison between single-agent and multi-agent approaches using traditional rule-based CLM systems, single-agent LLM approaches, and hybrid systems across standard contract types, varying complexity levels, and different user expertise patterns.

\textbf{User Study Validation:} Industry professional study with contract managers, legal professionals, and IT professionals using task-based evaluation scenarios, think-aloud protocols, post-task questionnaires, and comparative preference studies.

\textbf{Data Collection and Analysis:} Collection from system performance logs, user interactions, expert interviews, and benchmark datasets. Analysis using statistical methods for quantitative metrics, qualitative content analysis for user feedback, and comparative statistical tests.
